% LaTeX file for resume
% This file uses the resume document class (res.cls)

\documentclass[margin]{res}
\usepackage{url}
% the margin option causes section titles to appear to the left of body text
\textwidth=5.2in % increase textwidth to get smaller right margin
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font

\begin{document}

\name{Hawk Weisman\\[12pt]} % the \\[12pt] adds a blank line after name

\address{990 First St,\\ Meadville, PA, 16335  \\
        +1 (814) 853-1501}
\address{\url{hi@hawkweisman.me} \\ \url{http://hawkweisman.me}}


\begin{resume}

%\section{Objective}
%Auditing/Analysis of Operations

\section{EDUCATION}{\sl Bachelor of Science} in Applied Computing (Software Engineering)\\
                % \sl will be bold italic in New Century Schoolbook (or
                % any postscript font) and just slanted in
                % Computer Modern (default) font
                Allegheny College, Meadville, PA \\
                Degree expected: May 2016 \\
                GPA:\@ 3.67

                {\bf Relevant Coursework} \\
                \begin{ncolumn}{2}
                Data Structures and Algorithms  & Computer Organization \\
                Principles of Software Engineering & Operating Systems\\
                Principles of Data Management & Introduction to Compiler Design\\
                Programming Language Implementation & Robotics and Multi-Agent Systems\\
                Visual Computing
                \end{ncolumn}

% Tabulate Computer Skills; p{3in} defines paragraph 3 inches wide
\section{SKILLS}
   \begin{tabular}{l p{3in}}
                \textit{Proficient with} & Scala, Rust, Java, Python \\
                \textit{Capable with} & C, R, Lisp, SQL, HTML/CSS \\
                \textit{Familiar with} & Haskell, Go, CoffeeScript, JavaScript \\
                \textit{Web Frameworks}  & Scalatra, Bootstrap, Slick, JQuery \\
                \textit{Build and CI}  & Gradle, Ant, sbt, Make, Cargo, Travis, Jenkins \\
                \textit{Testing}  & ScalaTest, ScalaCheck, JUnit, Mockito\\
                \textit{IDEs/Editors}  &Atom, SublimeText, IntelliJ IDEA, Eclipse \\
                \textit{Source Control} &Git, GitHub, GitLab
 \end{tabular}


\section{WORK \\ EXPERIENCE}

        % {\sl Web Application Developer} \hfill  February 2015 --- Ongoing \\
        %         Carr Hall Garden, Allegheny College, Meadville, PA
        %          \begin{itemize}  \itemsep -2pt % reduce space between items
        %             \item Independently developed a web application for tracking inventory and sales data.
        %             \item Worked with the client to determine project requirements.
        %             \item Designed and developed web front-end and user interface, using HTML/CSS, JavaScript, JQuery, Bootstrap, and Jade.
        %             \item Designed and developed database-driven web back-end, using Scalatra, Slick, and H2DB.
        %          \end{itemize}

        {\sl Lead Software Engineer} \hfill  Spring 2014 --- Ongoing \\
        MeteorCode Laboratories, Meadville, PA
         \begin{itemize}  \itemsep -2pt % reduce space between items
            \item Co-founded a small business to develop and publish independently-developed computer games.
            \item Developed a game engine in Scala and Java, contributing a majority of source code to the project.
            \item Set up and maintained a development environment using GitLab, Jenkins CI, and Gradle.
\item Contributed to the design and development of a Web site, meteorcode.com, using HTML/CSS, SASS/SCSS, and Polymer.
         \end{itemize}

                %{\sl Aquaponics Technician} \hfill Winter Break 2013 \\
                %Environmental Science Department, Allegheny College, Meadville, PA
                % \begin{itemize}  \itemsep -2pt % reduce space between items
                %    \item Responsible for independently maintaining multiple decorative and production aquaponics systems.
                %    \item Performed maintenance tasks such as cleaning filters, feeding fish, and maintaining water levels.
                %\end{itemize}

                %{\sl Darkroom Technician} \hfill            2012-2013 \\
                %Art Department, Allegheny College
                % \begin{itemize}  \itemsep -2pt %reduce space between items
                %    \item Responsible for preparing chemicals and maintaining a well-stocked darkroom, as well as ensuring workspace cleanliness.
                %    \item Assisted and instructed art students in the use of darkroom materials and techniques.
                % \end{itemize}

                %{\sl Computer Art Studio Technician} \hfill        2012-2013 \\
                %Art Department, Allegheny College
                %  \begin{itemize} \itemsep -2pt %reduce space between items
                %   \item Instructed other students in the use of computer art tools, such as drawing tablets, digital video cameras, and large-format printers.
                %   \item Instructed other students in the use of software such as Photoshop, Illustrator, and Final Cut.
                %   \item Diagnosed and repaired technical difficulties with studio equipment.
                %   \end{itemize}
\section{SELECTED \\ PROJECTS}
        % {\sl Mnemosyne} \hfill Fall 2015 --- Ongoing
        % Allegheny College Senior Thesis \\
        % \url{https://github.com/hawkw/mnemosyne}
        % \begin{itemize} \itemsep -2pt
        %     \item Designed and prototyped a new functional language for systems programming.
        %     \item Wrote over
        % \end{itemize}

        {\sl Seax} \hfill Spring 2015 --- Ongoing \\
        Personal Project \\
        \url{http://hawkweisman.me/seax}
        \begin{itemize} \itemsep -2pt
            \item Designed and developed a runtime environment for functional programming languages.
            \item Implemented a virtual machine, Scheme compiler, and other utilities in Rust.
            \item Wrote over 3,500 lines of Rust code and over 3,000 lines of documentation.
        \end{itemize}

        {\sl Decaf Compiler} \hfill Fall 2014 \\
        CMPSC420: Introduction to Compiler Design, Allegheny College \\
        \url{https://hawkweisman.me/decaf}
        \begin{itemize} \itemsep -2pt % reduce space between items
        \item Worked on a team to develop a compiler for a small Java-like language.
        \item Contributed a majority of Scala source code
        \item Wrote unit tests using ScalaTest
        \item Developed parsing, semantic analysis, and Javabyte code generation components
        \end{itemize}

        {\sl DeeBee} \hfill Fall 2014 \\
        CMPSC380: Principles of Data Management, Allegheny College \\
        \url{https://github.com/hawkw/deebee}
        \begin{itemize} \itemsep -2pt % reduce space between items
        \item Independently developed a small SQL database for educational purposes
        \item Developed an architecture for a relational database implementation
        \item Wrote over 1,700 lines of Scala code
        \item Wrote unit tests using ScalaTest
        \end{itemize}

        {\sl Pathway Game Engine} \hfill Spring 2014 --- Ongoing \\
                MeteorCode Laboratories \\
        \url{https://github.com/MeteorCode/Pathway}
        \begin{itemize} \itemsep -2pt % reduce space between items
        \item Developed an open-source event driven game engine for the JVM platform.
        \item Implemented features such as file I/O, event system, and scripting systems.
        \item Contributed over 9,000 lines of Java and Scala source code.
        \item Designed an extensible architecture for a software development framework.
        \item Wrote a comprehensive test fixture using tools such as JUnit, Mockito, and JaCoCo.
        \end{itemize}

        {\sl Remote Collab SublimeText Plugin } \hfill Spring 2014 \\
        CMPSC440: Principles of Operating Systems, Allegheny College \\
        \url{https://github.com/TeamRemote/remote-sublime}
        \begin{itemize}  \itemsep -2pt % reduce space between items
            \item Developed an open-source SublimeText plugin to facilitate remote pair programming.
            \item Contributed over 1,000 lines of Python source code.
        \end{itemize}

        {\sl Filesystem Traversal Study} \hfill Spring 2014 \\
        CMPSC440: Principles of Operating Systems, Allegheny College \\
        \url{https://github.com/hawkw/traverse}
         \begin{itemize} \itemsep -2pt % reduce space between items
            \item Independently organized a research project to collect and analyze filesystem data.
            \item Programmed data-collection tools in Python.
            \item Prepared an IPython notebook to analyze and visualize data.
            \item Encouraged other students to voluntarily contribute datasets.
        \end{itemize}


\section{REFERENCES}
{\sl Dr. Janyl Jumadinova} \hfill \\
Assistant Professor \\ Department of Computer Science \\ Allegheny College \\
\url{jjumadinova@allegheny.edu} \\
+1 (814) 332-2881 \\

{\sl Dr. Gregory Kapfhammer} \hfill \\
Associate Professor and Chair \\ Department of Computer Science \\ Allegheny College \\
\url{gkapfham@allegheny.edu} \\
+1 (814) 332-2880\\
%
% {\sl Kerstin Martin} \hfill \\
% Carr Hall Garden Manager \\ Allegheny College \\
% \url{kmartin@allegheny.edu} \\
% +1 (814) 332-2787\\


\end{resume}
\end{document}
